### 2017-08-03 Tex_Dissertation/MSc_dissertation.tex
n

>>>>

There are various ways that have been developed for the calculation of the squark masses at electron-positron
linear colliders. In this chapter I present one that will not be used in my analysis but sketch the potencial
and thus the importance of the aforementioned colliders regarding these kind of calculations.

The main topologies that are considered are those that the gluino is heavier than the squarks and thus the 
dominant decaying channel is:

\begin{equation}
 e^{-}e^{+} \rightarrow \tilde{q} \tilde{\bar{q}} \rightarrow q\bar{q}\chi_{1}^{0}\chi_{1}^{0}
\end{equation}

It needs to be mentioned that a powerfull advantage of the CLIC experiment is the possibility of achieving 
polarisation up to 80$\%$ helping to reduce the WW background and the ability to create right or left squarks
depending on the needs of the physical analysis.

\subsection{Modified Invariant Mass}

This technique has been developed initially for LHC experiment where the p-p collision energy is not known.
The calculation was achieved by creating the variable $M_{C}$ which is related to the standard 
invariant mass but it's invariance comes from contra linear boosts of equal magnitude. The squark mass is given
by:

\begin{equation}
 m_{\tilde{q}}=\frac{1}{2} \big(M_{C}^{max} + \sqrt{(M_{C}^{max})^{2} + 4m_{\chi}^{2}} \big)
\end{equation}

where

\begin{equation}
 M_{C}^{2}=2(E_{q,1}E_{q,2}+\vec{p}_{q,1}\vec{p}_{q,2})
\end{equation}

and

\begin{equation}
 M_{C}^{max}=\frac{m^{2}_{\tilde{q}}-m^{2}_{\chi}}{m_{\tilde{q}}}
\end{equation}

The power off this kind of calculation comes from the fact that no knowledge for the exact center of mass 
energy is needed (In comparison with the first method described in~\cite{simon2010techniques}), something that is not purely known since the effects of initial state radiation and
the Beamstrahlung can distort it significantly resulting to even bigger uncertainties. Note that this method 
assumes that the mass of the neutralino is known and that the quark is massless.

\section{Minimisaton of $\chi^{2}$ Method}

In this chapter I describe the procedure that I followed until the calculation of the top squark mass. 
This involved the vertex finding, the jet clustering, the flavourtagging and the calculation of the $\chi^{2}$
for each top squark mass.

\subsection{Vertex Finding}

For the needs of this projecct I used the package of LCFIplus which is an improved software of the already 
existing one LCFIVertex. The important difference between the  two is that LCFIplus employs the vertex finding 
befere the jet clustering (in comparison to LCFIVertex which follows the exact oposite procedure) with the 
goal to protect the secondadry vertices from breaking up and grouped into different jets~\cite{suehara2016lcfiplus}.
This is an important step towards better performance since the Bottom jets can be identified from their 
sufficiently large distance between the primary vertex and their decay vertex. Additionally, the importance
of this step to be performed before jet clustering, is that hadrons that contain bottom or charm quarks 
have sizeable lifetimes and they can be measured Inside the detector.

That said, the vertex finding was the first step towards obtaining the final data for analysis.

\subsection{Jet Clustering}

Jets are an indespensible part of high energy physics. They come from the manifestation of strong nuclear
as free quarks or gluons hadronize. They are visual structures that are measured in the detectors and they
serve the need of approaching the initial parton that they originated. Throught the years various algorithms 
have been developed for the clustering of such objects differing in the way that the approach suchh procedure.
Two of the most famous are the sequential recombination algorithms and cone algorithms. In this projecct I use
the a sequential recombination algorithm, the $k_{t}$ algorithm which is a longitudinaly invariant algorithm
firstly designed for hadron colliders.

The $k_{t}$ involves a measure of distance $d_{ij}$ for all the pair of particles $i,j$:

\begin{equation}
 d_{ij}=d_{ji}=min(p_{Ti}^{2},p_{Tj}^{2})\frac{\Delta R^{2}_{ij}}{R^{2}}
\end{equation}

where $p_{Ti}$ is the transverse momentum of $i^{th}$ particle with respect to beam direction and 
$\Delta R^{2}_{ij}=(y_{i}-y_{j})^{2}+(\phi_{i}-\phi_{j})^{2}$ with $y$ being the rapitdity, $\phi$ being
the azimuth angle and R the jet radius fixed in this project as $R=0.7$.

The basic idea behind this algorithm is that it calculates the $d_{ij}$ with the smallest value and then it 
"merges" the $i,j$ into a single object with momentum $p_{i}+p_{j}$. This procedure is repeated until the quantity
$d_{ij}$ is above some threshold and all the particles that are left are the event's jet
~\cite{cacciari2012fastjet}.

\subsection{Flavour Tagging}
